Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-15 Paper/ms.tex
Caption words

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_posterior.eps}
\caption{The joint posterior distribution for the periods and the amplitudes
(top panel) and the periods and eccentricities (bottom panel).
\label{fig:fake_data_posterior}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_posterior.eps}
\caption{The joint posterior distribution for the periods and the amplitudes
(top panel) and the periods and eccentricities (bottom panel) from the
simulated dataset. The true values are plotted as circles.
\label{fig:fake_data_posterior}}
\end{figure}
